### 2016-05-30 paper/rebuttal.tex

% #BIBTEX /Library/Tex/texbin/bibtex eccv2016
% last updated in April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
% \usepackage{tensor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{ulem}
\usepackage{url}
\usepackage{cite}

\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}

\newcommand{\mysubsubsection}[1]{\vspace{0.2cm} \noindent
  \underline{{\bf #1}} \vspace{0.1cm}}
\newcommand{\mysubsubsubsection}[1]{\vspace{0.1cm} \noindent {\bf #1}:}

% \newcommand{\pushmeet}[1]{\textcolor{blue}{pushmeet:{#1}}}
% \newcommand{\yasu}[1]{\textcolor{magenta}{[yasu: {#1}]}}
\newcommand{\chen}[1]{\textcolor{cyan}{[chen: {#1}]}}
% \newcommand{\hang}[1]{\textcolor{green}{[hang: {#1}]}}
% \newcommand{\pushmeet}[1]{}
% \newcommand{\chen}[1]{}
% \newcommand{\yasu}[1]{}
% \newcommand{\hang}[1]{}

\ifx\pdfoptionalwaysusepdfpagebox\relax\else
\pdfoptionalwaysusepdfpagebox5
\fi

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV16SubNumber{1569}  % Insert your submission number here

% \title{Parallelizing Hypothesis Fusion for Rapid MAP inference}
\title{Multi-way Particle Swarm Fusion}

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
We thank the reviewers for insightful comments. Major comments are
the limitation of using only 4 threads and the problem specific choice of architectures. We first address these major comments.

\vspace{0.15cm}
\noindent {\bf The lack of technical contribution:} We
believe that this paper proposes an effective parallel
framework which, based on the novel concept of solution
sharing and multi-way fusion, generalizes several existing
methods. With simple parameter tuning, our framework can be
specialized as an effective parallel architecture for any
given MRF inference tasks. We will also make our framework implementation public, so that researchers can utilize maximum parallelism by simply providing the energy function and solution proposals. So the
impact of this work would be huge.

\vspace{0.15cm}
\noindent {\bf The choice of architectures:} We agree with
R1 and R3 that the best fusing architecture is problem
specific. However, our parallel framework is general,
achieving all the architectures mentioned in the paper via
different parameter settings. This is indeed an advantage of
our framework because the best architecture can be found by
simple grid search over parameter space in the same
framework instead of trying various existing methods. And
existing methods, as the special cases of our framework, are
very unlikely to be the best architecture for any problem
settings. Note that there are only three parameters
($\alpha$, $\beta$, and the frequency of solution sharing)
controlling the parallel architecture, and all these three
are small integer numbers, so the grid search space can be
easily conducted. Note that in order to illustrate the
intuition behind solution sharing and multi-way fusion, we
only presented three special architecture of our framework
in the paper, namely SF-SS, SF-MF, and SF (despite of its
name, we use maximal solution sharing and multi-way fusion
in all our experiments). But to solve a
problem in practice, a grid search is required to find the best
parameter setting. We will add the discussion here to the
paper and provide codes for automatic parameter tuning.

\vspace{0.15cm} We believe that this paper proposes a novel
parallel framework which will benefit many researchers with
more effective parallel architectures over existing
methods. The best architecture for any given problem can be
found via simple grid search in the parameter space. Now, we
answer remaining questions from each reviewer. We will
clarify these points in the paper, too.

\vspace{0.15cm}
\noindent {\bf Reviewer 1}

\vspace{0.15cm}
\noindent $\bullet$ (The number of threads:) Note that the
complexity for each thread is independent of the number of
threads in total. With this nature, we can apply our
parallel scheme to any number of threads or even distributed
systems. To make comparison fair in our experiments, we only
use 4 threads to make sure all threads including the
additional monitor thread run on its own physical core. The
experiments focus more on the intuition behind solution
sharing and multi-way fusion instead of pursuing best performance. But in
practice, our current implementation allows the usage of any
number of threads. A future work would be implementing our
parallel scheme on distributed environments.

\noindent $\bullet$ (Compliants about Fig. 3:) Thanks for
pointing it out. This figure is indeed incomplete as we want
to stress speed difference and explain this intuition of
solution sharing. The complete figure is shown in Fig. 1
here. As the energy is submodular in this problem setting,
all the architectures can find the global minimum at the
end.

\noindent $\bullet$ (Line 416-417 statement contradicts SF-MF in Fig. 1:) As indicated by the red arrows, the last thread of SF-MF on the figure (far right) also explores solutions generated by other thread (which is not shown on the figure). We will make the figure more clear.

\noindent $\bullet$ (Underlining paragraph titles:) Thanks for pointing it out. We will change the format.

% \section{R2}
\vspace{0.15cm}
\noindent {\bf Reviewer 2}
\noindent $\bullet$ (Missing reference:) We thank R2 for
pointing out this paper, Simultaneous Fusion Moves for
3D­Label Stereo. However, to our understanding, the
multi-label fusion move proposed in this paper is different
with out multi-way fusion. Their multi-label fusion move
conduct one single TRW inference (with many iterations) to
fuse all proposals together, whereas our multi-way fusion
conduct one TRW inference to fuse only a subset of proposals
and repeat the fusion until convergence. When the energy
function becomes more complex or the number of proposals is
large, a single TRW over all proposals is very hard to
converge, but our multi-way fusion will still work by
repeatedly fusing small subset of proposals.

\chen{\noindent $\bullet$ (The benefit of multi-threading:)
  We admit that the multi-threading does not help the
  algorithm for some applications if run to
  convergence. However, it consistently benefits online
  optimization as it provides better results at each
  timestamp.}

\vspace{0.15cm}
\noindent {\bf Reviewer 3}

\noindent $\bullet$ (The intuition behind Swarm Fusion:) We
illustrate the benefit of utilizing solution sharing and
multi-way fusion through experiments and explain the
intution behind. The Swarm Fusion combines both ideas and is
a general scheme. These two ideas are intuitive and
effective. We are not aware of other relevant ideas.

\noindent $\bullet$ (Lack of exciting results:) We
appreciate the comment that some results we show are not
exciting. However, our experiments use extreme cases to
illustrate the idea of solution sharing and multi-way
fusion. While in practice, the best parameter setting is
unlikely to be any of these extreme cases and should be
found by a grid search over parameter space. However,
instead of achieving the best performance, we are more
excited about the effectivenss and applicability of our
framework, which makes it a handy tool for speeding up many
MRF inference problem. We will add relevant discussion in
the paper.

\noindent $\bullet$ (Dependent on proposal generations:) We
agree with R3 that the performance is highly dependent on
proposal generation scheme. This fact causes trouble for
fair comparison as some proposals are not applicable or
despite certain architectures. To make the comparison fair,
we often discard certain proposal generation schemes
in the cost of performance.

\noindent $\bullet$ (Proposal generation schemes from [15]:) \chen{I am not sure what this compliant is about as none of our experiments is about [15]}

\end{document}

### 2017-01-27 paper/rebuttal.tex

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
We thank the reviewers for insightful comments. Major comments are
the limitation of using only 4 threads and the problem specific choice of architectures. We first address these major comments.

\vspace{0.15cm}
\noindent {\bf The lack of technical contribution:} We
believe that this paper proposes an effective parallel
framework which, based on the novel concept of solution
sharing and multi-way fusion, generalizes several existing
methods. With simple parameter tuning, our framework can be
specialized as an effective parallel architecture for any
given MRF inference tasks. We will also make our framework
implementation public, so that researchers can utilize
maximum parallelism by simply providing the energy function
and solution proposals. So the impact of this work would be
huge.

\vspace{0.15cm}
\noindent {\bf The choice of architectures:} We agree with
R1 and R3 that the best fusing architecture is problem
specific. However, our parallel framework is general in the
sense that it achieves all the architectures mentioned in
the paper via different parameter settings. This is indeed
one advantage of our framework because the best architecture
can be found by a simple grid search over parameter space in
the same framework instead of trying various existing
methods. And existing methods, as the special cases of our
framework, are very unlikely to be the best
architecture. Note that there are only three parameters
($\alpha$, $\beta$, and the frequency of solution sharing)
controlling the parallel architecture, and all these three
are small integer numbers, so the grid search can be
easily conducted. Note that, in order to illustrate the
intuition behind solution sharing and multi-way fusion, we
only presented three special architecture of our framework
in the paper, namely SF-SS, SF-MF, and SF (despite of its
name, we use maximal solution sharing and multi-way fusion
in all our experiments). But to solve a problem in practice,
a grid search is required to find the best parameter
setting. We will add the discussion to the paper and
provide codes for automatic parameter tuning.

@@

\vspace{0.15cm} We believe that this paper proposes a novel
parallel framework which will benefit many researchers with
more effective parallel architectures over existing
methods. The best architecture for any given problem can be
found via simple grid search in the parameter space. Now, we
answer remaining questions from each reviewer. We will
clarify these points in the paper, too.

\vspace{0.15cm}
\noindent {\bf Reviewer 1}

\vspace{0.15cm}
\noindent $\bullet$ (The number of threads:) Note that the
complexity for each thread is independent of the number of
threads in total. With this nature, we can apply our
parallel scheme to any number of threads or even distributed
systems. To make comparison fair in our experiments, we only
use 4 threads to make sure all threads including the
additional monitor thread run on its own physical core. The
experiments focus more on the intuition behind solution
sharing and multi-way fusion instead of pursuing best performance. But in
practice, our current implementation allows the usage of any
number of threads. A future work would be implementing our
parallel scheme on distributed environments.

\noindent $\bullet$ (Compliants about Fig. 3:) Thanks for
pointing it out. This figure is indeed incomplete as we want
to focus on speed difference and explain this intuition behind
solution sharing. As the energy is submodular in this problem setting,
all the architectures can find the global minimum at the
end. We will add the complete graph to the paper.

@@

\noindent $\bullet$ (Line 416-417 statement contradicts SF-MF in Fig. 1:) As indicated by the red arrows, the last thread of SF-MF on the figure (far right) also explores solutions generated by other thread (which is not shown on the figure). We will make the figure more clear.

\noindent $\bullet$ (Underlining paragraph titles:) Thanks for pointing it out. We will change the format.

% \section{R2}
\vspace{0.15cm}
\noindent {\bf Reviewer 2}
\noindent $\bullet$ (Missing reference:) We thank R2 for
pointing out this paper, Simultaneous Fusion Moves for
3D­Label Stereo. However, to our understanding, the
multi-label fusion move proposed in this paper is different
with out multi-way fusion. Their multi-label fusion move
conducts one single TRW inference (with many iterations) to
fuse all proposals together, whereas our multi-way fusion
conducts one TRW inference to fuse only a subset of proposals
and repeat the fusion until convergence. When the energy
function becomes more complex or the number of proposals is
large, a single TRW over all proposals is very hard to
converge, but our multi-way fusion will still work well by
repeatedly fusing small subset of proposals.

@@

\chen{\noindent $\bullet$ (The benefit of multi-threading:)
  We admit that the multi-threading does not help the
  algorithm for some applications if run to
  convergence. However, it consistently benefits online
  optimization as it provides better results at each
  timestamp.}

\vspace{0.15cm}
\noindent {\bf Reviewer 3}

\noindent $\bullet$ (The intuition behind Swarm Fusion:) We
illustrate the benefit of utilizing solution sharing and
multi-way fusion through experiments and explain the
intution behind. The Swarm Fusion combines both ideas and is
a general scheme. These two ideas are intuitive and
effective. We are not aware of other relevant ideas.

\noindent $\bullet$ (Lack of exciting results:) We
appreciate the comment that some results we show are not
exciting. However, our experiments use extreme cases to
illustrate the idea of solution sharing and multi-way
fusion. While in practice, the best parameter setting is
unlikely to be any of these extreme cases and should be
found by a grid search over parameter space. However,
instead of achieving the best performance, we are more
excited about the effectivenss and applicability of our
framework, which makes our framework a handy tool for speeding up many
MRF inference problems. We will add relevant discussion in
the paper.

### 2017-01-27 paper/rebuttal.txt

We thank the reviewers for insightful comments. Reviewers are overall in favor of the idea, but are concerned that 1) the optimal architecture depends on each problem, and 2) the performance still depends on a problem-specific proposal generation scheme.
 
We now regret the way we presented our work, as these factors exactly demonstrate the strength of our approach. We have presented an approach that unifies  different move making algorithms in one common parallelized framework for MAP inference. In our experiments, three hyper-parameters (alpha, beta, and the frequency of solution sharing) control the architecture. A research can employ a simple grid-search (or more sophisticated Bayesian optimization) over these hyper-parameters to identify the architecture best suited for a given problem. Our latest experiments have confirmed that the grid search can indeed identify the optimal configuration under certain measurement for each problem within 100 search iterations.

We presented three particular architectures in the paper to 1) distinguish the effects of the solution-sharing and the multi-way fusion; and 2) avoid unfair comparisons against existing methods that cannot optimize architectures. However, we agree with the reviewers that the process of finding the architecture (and its unfairness) is an important aspect of the work.

We also agree that our approach still relies on problem-specific proposal generation schemes. However, this is true to any other existing methods. We need problem-specific proposals to solve challenging problems, which cannot be solved by a general-purpose method. This framework can quickly find the optimal hyper-parameters and the architecture for you, given a proposal generation scheme.

We will modify the paper to address all these points and add the hyper-parameter optimization algorithm (less than 10 lines) and its results. We hope to convince R1 and R3 that this paper presents a rather unique holistic view and parameterization of the parallel inference algorithm family. The idea is easy to understand and implement with immediate impact to every Computer Vision researcher or engineer, who currently solves a challenging graphical model inference problem.

We now address the remaining concerns from the reviewers.

The number of threads: Our parallel scheme can be applied to any number of threads or even distributed systems. We also did experiments on 8 threads and had same observations. That is, solution sharing speeds up convergence in most experiments and multi-way fusion can find lower energy in complex problem settings. We will show experiment results on 8 threads in the paper as utilizing 8 threads has a larger impact. A future work would be implementing our parallel scheme on distributed systems.

Incomplete Fig. 3: We only show part of the figure to put speed difference in focus. As the energy is submodular in this problem setting, all the architectures can find the global minimum at the end. We will show the complete graph in the paper.

SF-MF in Fig. 1: As indicated by the red arrows, the last thread of SF-MF on the figure also explores solutions generated by another thread (which is not shown). We will clarify the figure.

Missing reference: We thank R2 and will cite it. But note that their multi-label fusion move is different with our multi-way fusion. They conduct only one TRW inference to fuse all proposals at once and call each iteration a move, whereas we conducts one TRW inference (a move) to fuse only a subset of proposals and repeat the fusion until convergence. This strategy makes our method applicable to problem with more complex energy or larger number of proposals.

Intuition behind Swarm Fusion: We confirm the benefit of solution sharing and multi-way fusion in our experiments. The Swarm Fusion is a general scheme incorporating both ideas. We are not aware of other intuitive ideas.

Lack of exciting results: We use extreme cases to illustrate the idea of solution sharing and multi-way fusion. While in practice, the best parameter setting is unlikely to be any of these extreme cases and should be found by a grid search.
